Sustained software development, not number of citations or journal choice, is indicative of accurate bioinformatic software

### 2021-08-16 manuscript/supplementary.tex
Updating/adding figures, supplementary materials and minor manuscript edits.

\begin{figure}[H]
\centering
\includegraphics[width=0.95\textwidth]{supplementary-figures-pairs.pdf}
\caption{Dot plots for each feature relative to every other feature
  (accuracy, speed, JH5, citations, H-index, M-index, relAge,
  relCites, yearPublished, version, commits, contributors,
  ).

}
\label{fig:metricPairs}
\end{figure}

@@

\begin{figure}[H]
\centering
%\includegraphics[width=0.95\textwidth]{relAge-SpeedVsAccuracy-heatmap-edited.pdf}
\includegraphics[width=0.45\textwidth]{relAge-speedAcc.pdf}
\includegraphics[width=0.45\textwidth]{relAge-SpeedVsAccuracy-heatmap.pdf}
\caption{{\bf Relative software tool ages and speeds/accuracies.} {\bf Left.} Violin plots for the relative age distribution
  for software tools in each of the 5 2x2 cells indicated in B. The
  five boxes correspond to the four extreme corners of the speed vs
  accuracy spectrum (i.e. slow and inaccurate, slow and accurate, fast
  and inaccurate, fast and accurate) and the central box (medium speed
  and medium accuracy). {\bf Right.} A heatmap indicating the relative age
  of software in a range of relative accuracy and speed rankings. Blue
  colours indicate an abundance of older software tools in an accuracy
  and speed category, while light colours indicate younger software in
  an accuracy and speed category. }
\label{fig:ageplot}
\end{figure}

>>>>

\begin{figure}[H]
\centering
\includegraphics[width=0.95\textwidth]{supplementary-figures-pairs.pdf}
\caption{Dot plots for each feature relative to every other feature
  (accuracy, speed, JH5, citations, H-index, M-index, relAge,
  relCites, yearPublished, version, commits, contributors, \#Issues,
\%Open issues, \#Pull requests, and the \#Forks).
}
\label{fig:metricPairs}
\end{figure}

@@

\begin{figure}[H]
\centering
%\includegraphics[width=0.45\textwidth]{relAge-speedAcc-jitterPlot.pdf}
%\includegraphics[width=0.45\textwidth]{relAge-SpeedVsAccuracy-heatmap.pdf}
\includegraphics[width=0.95\textwidth]{relAge.pdf}
\caption{{\bf Relative software tool ages and speeds/accuracies.}
{\bf A.} A heatmap indicating the relative age
  of software in a range of relative accuracy and speed rankings. Blue
  colours indicate an abundance of older software tools in an accuracy
  and speed category, while light colours indicate younger software in
  an accuracy and speed category.
  {\bf B.} Jitter-plots for the relative age distribution
  for software tools in each of the 5 3x3 cells indicated in {\bf B}. The
  five row correspond to the four extreme corners of the speed vs
  accuracy spectrum (i.e. slow and inaccurate, slow and accurate, fast
  and inaccurate, fast and accurate) and the central box (medium speed
  and medium accuracy). Median, quartile and extreme values are indicated with tick marks for each group.
  Accurate and fast software tools tend to have been published more recently than inaccurate and slow tools (Wilcox rank sum test, $W=341,~P=5\times 10^{-3}$)
   }
\label{fig:ageplot}
\end{figure}
